Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-06-30 conclusions.tex
minor rewording of first sentence of conclusion
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1244 ccdd05d5-56c1-461a-bf98-85f6876523b4

We have demonstrated a computationally feasible procedure for the rapid and
even early-warning filtering of data for \GW{}s emitted during the coalescence
of neutron stars and stellar-mass black holes.  It is one part of a complicated
analysis and observation strategy that will unfortunately have other sources of
latency.  However, we hope that it will motivate further work to reduce such
technical sources of \GW{} observation latency and encourage the possibility of
even more rapid \EM\ followup observations to catch prompt emission in the
advanced detector era.

>>>>

We have demonstrated a computationally feasible filtering algorithm for the rapid and
even early-warning detection of \GW{}s emitted during the coalescence
of neutron stars and stellar-mass black holes.  It is one part of a complicated
analysis and observation strategy that will unfortunately have other sources of
latency.  However, we hope that it will motivate further work to reduce such
technical sources of \GW{} observation latency and encourage the possibility of
even more rapid \EM\ followup observations to catch prompt emission in the
advanced detector era.
